Gazing at a Robot's Head Reflects our Tendency to Anthropomorphise

### 2016-09-06 main.tex
WIP on discussion

\rightheader{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Gazing at the Robot's Head Reflects our Tendency to Anthropomorphise}

@@

Lastly, we investigated one of the dynamics of anthropomorphic projections: is
watching a specific robot after a human-like cognitive priming sufficient to
impact the \emph{general} perception of robots as anthropomorphic agents. By
administrating the same Godspeed questionnaire as a post-test, we computed 
\deltaant to assess possible change in the participants' general tendency to
anthropomorphise. The stimuli were short videos of `toy' interaction scenarios,
and we did not anticipate any transfer of the anthropomorphic traits ascribed onto
the robot seen in the videos, to the broader tendency to anthropomorphise
robots in general, as assessed in the post-questionnaire. Our result challenge
this assumption: \deltaant is significantly higher for the participants who have been
primed with higher cognitive expectation before watching the robot performing
the tasks. This suggests a form of transfer: participants changed somewhat their
minds about robots being with however

>>>>

\rightheader{Gazing at a Robot's Head Reflects our Tendency to Anthropomorphise}   % This should be the title, or a shortened version of the title if your title is long.
\leftheader{Lemaignan et al.}	  % For one or two authors, include both authors last names.  For three or more, use first author's last name et al.
\title{Gazing at a Robot's Head Reflects our Tendency to Anthropomorphise}

@@

Lastly, we investigated one of the dynamics of anthropomorphic projections: is
watching a specific robot after a human-like cognitive priming sufficient to
impact the \emph{general} perception of robots as anthropomorphic agents. By
administrating the same Godspeed questionnaire as a post-test, we computed
\deltaant to assess possible change in the participants' general tendency to
anthropomorphise. The stimuli were short videos of `toy' interaction scenarios,
and we did not anticipate any transfer of the anthropomorphic traits ascribed
onto the robot seen in the videos, to the broader tendency to anthropomorphise
robots in general, as assessed in the post-questionnaire. Our result challenge
this assumption: \deltaant is significantly higher for the participants who have
been primed with higher cognitive expectations before watching the robot
performing the tasks. This suggests a form of transfer: participants changed
their minds about how human-like robots are from their perception of one
specific interaction situation with a specific robot. We did not test
how long this effect lasts (we suspect it might quickly decrease).
